Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review] {\bf Note that all references to appendices will be replaced with URLs in the final paper; they are appendices only for blind review.}}

### 2022-10-11 paper/Paper.tex
added image files and modified figure 9

    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, star/.style={circle, draw=red!60, fill=red!5, very thick, minimum size=1mm}]

    %Nodes
    \node[bignode](reg){\textbf{Reg}};
    \node[node](prop_var)[left=2 cm of reg]{Prop\_Var};
    \node[node](prop_cons)[below=of prop_var]{Prop\_Cons};
    \node[star](unary_star)[below=2 cm of reg]{};
    \node[node](reg_f)[below=of unary_star]{Reg\_F};
    \node[node](reg_g)[left= of reg_f]{Reg\_G};
    \node[star](temp_binary_star1)[right=2 cm of unary_star]{};
    \node[star](temp_binary_star2)[below= of temp_binary_star1]{};
    \node[node](reg_u)[below=of temp_binary_star2]{Reg\_U};
    \node[node](reg_r)[right=of reg_u]{Reg\_R};
    \node[star](prop_binary_star1)[right= of reg]{};
    \node[star](prop_binary_star2)[right= of prop_binary_star1]{};
    \node[node](join)[right=of prop_binary_star2]{Join};
    \node[node](set_intersect)[below=of join]{Set\_Intersect};

    %Lines
    \draw[->] (reg.west) -- (prop_var.east);
    \draw[->] (reg.south) -- (prop_cons.north);
    \draw[->] (reg.south) -- (unary_star.north);
    \draw[->] (unary_star.south) -- (reg_f.north);
    \draw[->] (unary_star.south) -- (reg_g.north);
    \draw[->] (reg.south) -- (temp_binary_star1.north);
    \draw[->] (reg.east) -- (prop_binary_star1.west);
    \draw[->] (temp_binary_star1.south) -- (temp_binary_star2.north);
    \draw[->] (temp_binary_star2.south) -- (reg_r.north);
    \draw[->] (temp_binary_star2.south) -- (reg_u.north);
    \draw[->] (prop_binary_star1.east) -- (prop_binary_star2.west);
    \draw[->] (prop_binary_star2.east) -- (join.west);
    \draw[->] (prop_binary_star2.south) -- (set_intersect.north);
    \end{tikzpicture}

>>>>

    \begin{tikzpicture}[ node/.style={rounded rectangle, draw=black!60, fill=black!5, thick, minimum size=10mm},
    bignode/.style={rounded rectangle, draw=black!60, fill=black!5, thick, minimum size=12mm},
    star/.style={circle, draw=red!60, fill=red!5, thick, minimum size=1mm} ]

    %Nodes
    \node[bignode] (reg) {\textbf{Reg}};
    \node[star](prop_binary_star1)[right= of reg]{};
    \node[star](prop_binary_star2)[right= of prop_binary_star1]{};
    \node[node](join)[right=of prop_binary_star2]{Join};
    \node[node](set_intersect)[below=0.5 cm of join]{Set\_Intersect};
    \node[node] (prop_var) [left=of reg] {Prop\_Var};
    \node[node] (prop_cons) [below=0.5 cm of prop_var] {Prop\_Cons};
    \node[star](unary_star)[below=0.9 cm of reg]{};
    \node[node](reg_f)[below=0.7 cm of unary_star]{Reg\_F};
    \node[node](reg_g)[left= of reg_f]{Reg\_G};
    \node[star](temp_binary_star1)[below=0.5 cm of prop_binary_star1]{};
    \node[star](temp_binary_star2)[below=0.5 cm of temp_binary_star1]{};
    \node[node](reg_u)[below=0.7 cm of temp_binary_star2]{Reg\_U};
    \node[node](reg_r)[right=of reg_u]{Reg\_R};

    %Lines
    \draw[->] (reg.west) -- (prop_var);
    \draw[->] (reg.south) -- (prop_cons);
    \draw[->] (reg.south) -- (unary_star);
    \draw[->] (unary_star.south) -- (reg_f.north);
    \draw[->] (unary_star.south) -- (reg_g);
    \draw[->] (reg.south) -- (temp_binary_star1);
    \draw[->] (reg.east) -- (prop_binary_star1.west);
    \draw[->] (temp_binary_star1.south) -- (temp_binary_star2.north);
    \draw[->] (temp_binary_star2.south) -- (reg_r);
    \draw[->] (temp_binary_star2.south) -- (reg_u.north);
    \draw[->] (prop_binary_star1.east) -- (prop_binary_star2.west);
    \draw[->] (prop_binary_star2.east) -- (join.west);
    \draw[->] (prop_binary_star2.south) -- (set_intersect);
    \end{tikzpicture}
